What We Eval in the Shadows

### 2021-04-15 paper/main.tex
Example of defer in withr
Adding an example of call capture with substitute

\todo{Add testthat or withr::defer\_handler (fancy on.exit)}

@@

\c{substitute} can be used to capture only a part of the call, \ie one of the arguments.

>>>>

Package \emph{withr} provides facilities to encapsulate side-effecting functions. The function \c{defer} is used to attach an expression to be evaluated when exiting any frame in the stack. It can be passed arbitrary code, and so blocks.

@@

\c{substitute} can be used to capture only a part of the call, \ie one of the arguments. For instance, in package \emph{xyplot}, the expression for argument \c{subset} is captured with \c{substitute} and then evaluated in a dataframe \c{data} and in the definition environment of \c{x}.
\begin{lstlisting}
 xyplot.formula <-  function(x,    data = NULL, ..., subset = TRUE)
 ...
subset <- eval(substitute(subset), data, environment(x))
\end{lstlisting}
